Delone lattice studies in \CIII, the space of three complex variables

### 2023-03-08 C3/C3.tex
C3 -- comment out section  title for graphics
C3 added graphics, sent to HJB

	\begin{synopsis}
		Selling reduction and Delone reduction are
		considered in a space of complex variables.
	\end{synopsis}
	\newcommand{\si}[0]{$s_1$}
	\newcommand{\sii}[0]{$s_2$}
	\newcommand{\siii}[0]{$s_3$}
	\newcommand{\siv}[0]{$s_4$}
	\newcommand{\sv}[0]{$s_5$}
	\newcommand{\svi}[0]{$s_6$}
	\newcommand{\Svec} [0] {\{\si, \sii, \siii, \siv, \sv, \svi \}}
	\newcommand{\SvecA} [0] {\{-\si, -\si+\sii, \si+\siii, \si+\sv, \si+\siv, \si+\svi \}}

@@

		The Delone scalars are studied in \CIII, the space of three complex variables.

@@

%	Although printing the image of a 6-dimensional object
%	is impossible, there is some utility to creating the
%	2-dimensional projections of \CIII{} onto the three
%	coordinates.

>>>>

	\begin{synopsis}
		The space \CIII{} is explained in more detail than
		in the original description. Boundary transformations
		of the fundamental unit are described in detail. 
		A graphical presentation of the basic coordinates
		is described and illustrated.
	\end{synopsis}
	\newcommand{\si}[0]{$s_1$}
	\newcommand{\sii}[0]{$s_2$}
	\newcommand{\siii}[0]{$s_3$}
	\newcommand{\siv}[0]{$s_4$}
	\newcommand{\sv}[0]{$s_5$}
	\newcommand{\svi}[0]{$s_6$}
	\newcommand{\Svec} [0] {\{\si, \sii, \siii, \siv, \sv, \svi \}}
	\newcommand{\SvecA} [0] {\{-\si, -\si+\sii, \si+\siii, \si+\sv, \si+\siv, \si+\svi \}}

@@

		The Delone (Selling) scalars, which are used in 
		unit cell reduction and in lattice type determination,
		are studied in \CIII, the space of 3 complex variables.
		The 3 complex coordinate planes are composed of the 6
		Delone scalars.

@@

	The 2-dimensional nature of the three coordinates of \CIII{} 
	suggests their use for graphical display.

	As an example, we use Phospholipase A2 (retrieved from 
	the Protein Data Bank \cite{Bernstein1977}), which has had several similar
	or identical structures determined \cite{LeTrong2007}. \citeasnoun{andrews2019b}
	found additional cases (see Table \ref{PLA2})

\begin{table}
	\begin{tabular}{l c c c c c c c c c}
		\toprule
		PDB id & Centering & a&b&c&$\alpha$&$\beta$&$\gamma$\\
		\midrule
	1DPY & R& 57.98& 57.98& 57.98& 92.02& 92.02& 92.02\\
	1FE5 & R& 57.98& 57.98& 57.98& 92.02& 92.02& 92.02\\
	1G0Z & H& 80.36& 80.36& 99.44& 90&    90&    120\\
	1G2X & C& 80.95& 80.57& 57.1 & 90&    90.35&  90\\
	1U4J & H& 80.36& 80.36& 99.44& 90&    90&    120\\
	2OSN & R& 57.10& 57.10& 57.10& 89.75& 89.75&  89.75\\
	\bottomrule
\end{tabular}	\\
\caption{Phospholipase A2 unit cells}
\label{PLA2}
\end{table}

Below, Figure \ref{fig1} shows the unit cells as 
reported (the centering of lattices has not been removed).
The following figures show various transformations and
embellishments of the reported cells.

\begin{figure}
	\includegraphics[width=1.0\textwidth]{1_35}
	\caption{Phospholipase A2 unit cells as reported. }
	\label{fig1}
\end{figure}

\begin{figure}
	\includegraphics[width=1.0\textwidth]{2_06}
	\caption{The unit cells Niggli reduced. The similarity 
	of the 3 projections is indicative of the exact or nearly
exact rhombohedral symmetry.}
	\label{fig2}
\end{figure}
\begin{figure}
	\includegraphics[width=1.0\textwidth]{3_03}
	\caption{The unit cells Delone reduced. }
	\label{fig3}
\end{figure}

\begin{figure}
	\includegraphics[width=1.0\textwidth]{4_13}
	\caption{The unit cells, Niggli and 5 copies were perturbed 2\%
	orthogonally to \SVI{} vector. }
	\label{fig4}
\end{figure}

\begin{figure}
	\includegraphics[width=1.0\textwidth]{5_21}
	\caption{The unit cells Niggli, and 5 copies were perturbed 10\%
		orthogonally to \SVI{} vector. }
	\label{fig5}
\end{figure}
